---
title: "P8105 Homework 1 by Ximeng"
output: html_document
---
Import the library tideverse
```{r}
library(tidyverse)
```

# PROBLEM 1

# Fisrt create a data frame
```{r}
problem1_df=tibble(
  samp = rnorm(10),
  logic_vec = samp>0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fac_vec = factor(c("s", "s", "s", "m", "m", "m", "m", "l", "l", "l"))
)

problem1_df 
```
 
# Try to take the mean of each variable

```{r}
mean(problem1_df$samp)
mean(problem1_df$logic_vec)
mean(problem1_df$char_vec)
mean(problem1_df$fac_vec)
```

# Covert variables to another type

```{r}
integer = as.integer(as.logical(problem1_df$logic_vec))
integer * problem1_df$samp
fact = as.factor(as.logical(problem1_df$logic_vec))
fact * problem1_df$samp
numb = as.numeric(as.factor(as.logical(problem1_df$logic_vec)))
numb * problem1_df$samp
```

# PROBLEM 2

# Load penguin data set
```{r}
data("penguins", package = "palmerpenguins")
```

# A short describtion of the data

The data set includes variables `r names(penguins)`.  The data set has `r nrow(penguins)` 
rows and `r ncol(penguins)` columns.  The mean of flipper length is 
`r mean(na.omit(penguins$flipper_length_mm))` mm.  



# Construct a scatterplot: flipper length (mm) vs bill length (mm), colored by species

```{r}
library(ggplot2)
ggplot(penguins, aes(x= flipper_length_mm, y= bill_length_mm, color = as.factor(species))) + geom_point()
```

# Save the plot

```{r}
ggsave("penguins.png", width = 5, height = 5)
```