---
title: "Homework 1 ximeng"
output: html_document
---

Import the library tideverse
```{r}
library(tidyverse)
```

# problem 1

#Fisrt create a data frame
```{r}
problem1_df=tibble(
  samp = rnorm(10),
  logic_vec = samp>0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fac_vec = factor(c("s", "s", "s", "m", "m", "m", "m", "l", "l", "l"))
)
```
 
# try to take the mean of each variable

```{r}
mean(problem1_df$samp)
mean(problem1_df$logic_vec)
mean(problem1_df$char_vec)
mean(problem1_df$fac_vec)
```

# covert variables to another type

```{r}
integer = as.integer(as.logical(problem1_df$logic_vec))
integer * problem1_df$samp
fact = as.factor(as.logical(problem1_df$logic_vec))
fact * problem1_df$samp
numb = as.numeric(as.factor(as.logical(problem1_df$logic_vec)))
numb * problem1_df$samp
```

# problem 2


```{r}
data("penguins", package = "palmerpenguins")
```

# short describtion

The data set includes variables `r names(penguins)`.  The data set has `r nrow(penguins)` 
rows and `r ncol(penguins)` columns.  The mean of flipper length is 
`r mean(penguins$flipper_length_mm)` mm.  



# Construct a scatterplot: flipper length (mm) vs bill length (mm), colored by species


```{r}
library(ggplot2)
ggplot(penguins, aes(x= flipper_length_mm, y= bill_length_mm, color = as.factor(species))) + geom_point()
```

#Save the plot

```{r}
ggsave("penguins.png", width = 30, height = 30)
```